\vspace{-0.25em}\thetitle

### 2009-07-28 paper.tex
...

This prediction technique, is clearly of immediate practical use:
applications range from network management to routing to quality of service.
Looking deeper than these immediate applications, however, the mere fact that this prediction technique works at all provides strong evidence that the underlying hypothesized model of flow behavior is valid.
Our future works will provide further applications and evidence by applying the same model to the problems of traffic classification and realistic workload generation.

The rest of this paper is organized as follows.
In \Section{background}, we provide some background and the present the observations which motivate this work.
Our model and hypothesis about flow behavior is presented in \Section{hypothesis}.
The experimental methodology for testing this hypothesis is presented in \Section{methodology}, and the results follow in \Section{results}.
\Section{discussion} discusses the meaning and impact of our results.
\Section{related-work} gives context for this work in relation other research.
We conclude with final remarks in \Section{conclusions}.

>>>>

This prediction technique is clearly of immediate practical use:
applications range from network management to routing to quality of service.
Looking deeper than these applications, however, the mere fact that this prediction technique works at all provides evidence that the underlying hypothesized model of flow behavior is valid.
Our future works will provide evidence and applications by applying this model to the problems of traffic classification and realistic workload generation.

The rest of this paper is organized as follows.
In \Section{background}, we provide some background and the present the observations which motivate this work.
Our model and hypothesis about flow behavior is presented in \Section{hypothesis}.
The experimental methodology for testing this hypothesis is presented in \Section{methodology} while the results follow in \Section{results}.
\Section{discussion} discusses the meaning and impact of our results and
\Section{related-work} gives context for this work in relation prior research.
We conclude with final remarks in \Section{conclusions}.
